Building a continuous benchmarking ecosystem in bioinformatics

### 2025-07-23 2_second_review/manuscript.tex
Deduplicate the cernvmfs section (by Mark) in both highlighted and normal tex

\item Software dependencies cause the biggest impact on replicability and maintainability; archiving all combinations of a large dependency tree, across several OS images, exponentially increases retention and maintenance costs. Making the long-term replicability of a benchmark tractable implies adopting a sane software management system. Several solutions exist, from containerization (e.g., \texttt{apptainer} or \texttt{Singularity}) \cite{Kurtzer2017-mn} and automation of reproducible and efficient software management (\texttt{EasyBuild} \cite{Hoste2012-gg} or \texttt{Spack} \cite{Gamblin2015-ll}) to distributing software installations such as CernVM-FS \cite{Blomer2013-jk},  or combinations of the two such as the Digital Research Alliance of Canada (former \texttt{computecanada}) \cite{Boissonneault2019-wm} and \texttt{EESSI} \cite{droge2023-ax}.

@@

The responsibility of handling software environments poses an interesting challenge to benchmarking systems. On one hand, some workflow managers provide means to install and activate software and re-run workflows when software specification changes, even if the workflow topology remains the same. For these, software is the workflow manager's responsibility. On the other hand, some benchmarks might be designed to compare the same workflow topology run with different software backends (i.e., with conda vs compiled) or with different versions of a dependency (e.g., samtools/htslib releases). Benchmarking systems should provide enough flexibility to make all variants possible (i.e., decouple the benchmark topology from the software backend).

Finally, scientific software management handling is known for its nuances, including abundant dependencies with known incompatibilities and complex installation recipes \cite{droge2023-ax}. Scientific software management is handled via traditional (Linux) package managers (RPMs, DEBs), central software stacks and environment modules (i.e., Lmod), conda, containers, or read-only network filesystems providing ready-to-use installations (CernVM-FS). These strategies are under active development: EESSI \cite{droge2023-ax} and the Digital Research Alliance of Canada \cite{Boissonneault2019-wm} are effectively providing multi-purpose, reusable and efficient software installations via CernVM-FS; \texttt{conda} is speeding up their deployment procedures (via \texttt{py-rattler}/\texttt{pixi}) and allowing compilation to Web assembly (to execute code within a web browser); and \texttt{apptainer} (former \texttt{Singularity}) provides rootless containerization suitable for running in scientific clusters.

>>>>

\item Software dependencies cause the biggest impact on replicability and maintainability; archiving all combinations of a large dependency tree, across several OS images, exponentially increases retention and maintenance costs. Making the long-term replicability of a benchmark tractable implies adopting a sane software management system.

@@

The responsibility of handling software environments poses an interesting challenge to benchmarking systems. On one hand, some workflow managers provide means to install and activate software and re-run workflows when software specification changes, even if the workflow topology remains the same. For these, software is the workflow manager's responsibility. On the other hand, some benchmarks might be designed to compare the same workflow topology run with different software backends (i.e., with \texttt{conda} vs compiled) or with different versions of a dependency (e.g., \texttt{samtools}/\texttt{htslib} releases). Benchmarking systems should provide enough flexibility to make all variants possible (i.e., decouple the benchmark topology from the software backend).

Finally, scientific software management handling is known for its nuances, including abundant dependencies with known incompatibilities and complex installation recipes \cite{droge2023-ax}. Scientific software management is handled via traditional (Linux) package managers (RPMs, DEBs), central software stacks and environment modules (i.e., Lmod), \texttt{conda}, containers (e.g., \texttt{apptainer} or \texttt{Singularity}; \cite{Kurtzer2017-mn}), or read-only network filesystems providing ready-to-use installations (CernVM-FS) \cite{Blomer2013-jk}. Further strategies are under active development: EESSI \cite{droge2023-ax} and the Digital Research Alliance of Canada \cite{Boissonneault2019-wm} are effectively providing multi-purpose, reusable and efficient software installations via CernVM-FS; \texttt{conda} is speeding up their deployment procedures (via \texttt{py-rattler}/\texttt{pixi}) and allowing compilation to Web assembly (to execute code within a web browser); and \texttt{apptainer} (former \texttt{Singularity}) provides rootless containerization suitable for running in scientific clusters.

### 2025-07-23 2_second_review/manuscript_with_tracked_changes.tex
Deduplicate the cernvmfs section (by Mark) in both highlighted and normal tex

\item Software dependencies cause the biggest impact on replicability and maintainability; archiving all combinations of a large dependency tree, across several OS images, exponentially increases retention and maintenance costs. Making the long-term replicability of a benchmark tractable implies adopting a sane software management system. Several solutions exist, from containerization (e.g., \texttt{apptainer} or \texttt{Singularity}) \cite{Kurtzer2017-mn} and automation of reproducible and efficient software management (\texttt{EasyBuild} \cite{Hoste2012-gg} or \texttt{Spack} \cite{Gamblin2015-ll}) to distributing software installations such as CernVM-FS \cite{Blomer2013-jk},  or combinations of the two such as the Digital Research Alliance of Canada (former \texttt{computecanada}) \cite{Boissonneault2019-wm} and \texttt{EESSI} \cite{droge2023-ax}.

>>>>

\item Software dependencies cause the biggest impact on replicability and maintainability; archiving all combinations of a large dependency tree, across several OS images, exponentially increases retention and maintenance costs. Making the long-term replicability of a benchmark tractable implies adopting a sane software management system. {\color{red} \sout{ Several solutions exist, from containerization (e.g., \texttt{apptainer} or \texttt{Singularity}) \cite{Kurtzer2017-mn} and automation of reproducible and efficient software management (\texttt{EasyBuild} \cite{Hoste2012-gg} or \texttt{Spack} \cite{Gamblin2015-ll}) to distributing software installations such as CernVM-FS \cite{Blomer2013-jk},  or combinations of the two such as the Digital Research Alliance of Canada (former \texttt{computecanada}) \cite{Boissonneault2019-wm} and \texttt{EESSI} \cite{droge2023-ax}.}}
